Leaf traits drive differences in biomass partitioning among major plant functional types

### 2015-07-23 manuscript.Rnw
Automatic word count on first page

@@

\section*{Abstract}

@@

Because of allometric relationships between the studied variables \citep{niklas1994}, there was a strong effect of plant height on LMF (Fig. 2a and S2). When corrected for plant height by estimating LMF at a common plant height, we found that LMF was proportional to the average leaf mass per area (LMA) across the three PFTs (Fig. 2b). As a consequence, LAR was invariant between PFTs, because LAR = LMF / LMA (Fig. 2c and S3). Mirroring the results for LMF, we found that the amount of leaf mass per unit stem area ($M_F/A_S$) differs among the three PFTs, that these differences are also proportional to LMA (Fig. 2d), and that PFTs are similarly invariant in the amount of leaf area per unit stem area ($A_F/A_S$) (Fig. 2e).

>>>>

Total number of words: \Sexpr{nrw$Total} \\
Abstract: \Sexpr{nrw$Abstract} \\
Introduction: \Sexpr{nrw$Introduction} \\
Methods and Materials: \Sexpr{nrw$Methods} \\
Results: \Sexpr{nrw$Results} \\
Discussion: \Sexpr{nrw$Discussion} \\

Number of figures: 4 (all in colour) \\
Number of tables: 1 \\
Supporting information : 5 Tables, 5 Figures and 1 Notes.

@@

\clearpage
\section*{Abstract}

@@

Because of allometric relationships between the studied variables \citep{niklas1994}, there was a strong effect of plant height on LMF (Fig. 2a and Fig. S2). When corrected for plant height by estimating LMF at a common plant height, we found that LMF was proportional to the average leaf mass per area (LMA) across the three PFTs (Fig. 2b). As a consequence, LAR was invariant between PFTs, because LAR = LMF / LMA (Fig. 2c and Fig. S3). Mirroring the results for LMF, we found that the amount of leaf mass per unit stem area ($M_F/A_S$) differs among the three PFTs, that these differences are also proportional to LMA (Fig. 2d), and that PFTs are similarly invariant in the amount of leaf area per unit stem area ($A_F/A_S$) (Fig. 2e).
